Time-variable surface mapping of exoplanets: an application to Io

### 2020-10-08 paper/paper.tex
minor changes to abstract

\begin{abstract}
Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
Existing photometric observations in the near infrared taken during occultations by Jupiter and Galilean moons encode a wealth of information about its surface.
Io is thus an ideal testbed for models of time-variable exoplanet surfaces.
We built a generative model of Io's surface for each observation using Nonnegative Matrix Factorization.
The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and also computes exact gradients with respect to all input parameters.
We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
While we mostly focus on Io, the models are directly applicable to mapping exoplanets.
We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}

>>>>

\begin{abstract}
Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
Existing photometric observations in the near infrared taken during occultations by Jupiter and Galilean moons encode a wealth of information about its surface.
Io is thus an ideal testbed for models of time-variable exoplanet surfaces.
We built a generative model of Io's surface for each observation using Nonnegative Matrix Factorization.
The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and exact gradients with respect to all input parameters.
We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
While we mostly focus on Io, our models are directly applicable to mapping exoplanets.
We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
